Preparing a manuscript for a peer-reviewed journal the FMDL way

### 2021-08-04 IITD_Manuscript.tex
Updated acknowledgments with statement of contributions and CRediT taxonomy

Authors FA, TA, PS and MS declare competing interest in the form of an Indian patent application (2021345678).

>>>>

\subsection*{Statement of contributions}

FA fabricated the devices. FA and TA characterized devices. SA and PS synthesized active semiconductor materials. SA, TA, and PS carried out XPS measurements. FA, SA, TA, and PS carried out data reduction. FA, SA, PS, CP and MS carried out technical discussions. FA, SA, CP and MS wrote the manuscript.

As per \href{https://casrai.org/credit/}{CRediT} taxonomy: a) Conceptualization: FA, CP and MS, b) Data curation: FA, SA, TA, and PS, c) Formal analysis: FA and PS, d) Funding acquisition: CP and MS, e) Investigation: FA, SA, TA, and PS, f) Methodology: PS, CP and MS, g) Project administration: PS, CP and MS, h) Resources: CP and MS, i) Software: FA, SA and PS, j) Supervision: PS, CP and MS, k) Validation: FA and TA, l) Visualization: FA, SA, TA, and PS, m) Writing - original draft: FA and SA, n) Writing - review \& editing: FA, CP and MS.

\subsection*{Conflicts of Interest}
Authors FA, TA, PS and MS declare competing interest in the form of an Indian patent application (2021345678).
